**The status of the microbial census: an update**

### 2015-12-03 doc/notebook/Bacterial_data_acquisition.Rmd
Add steps to process extra EMIRGE data

@@

>>>>

## EMIRGE sequence data

EMIRGE is a method of either assembling 16S rRNA gene sequences from metagenomic
data or from sheared amplicons. This is a method of generating full-length
sequences using short read technologies. We've identified a handful of studies
that have used EMIRGE to generate these data and that actually made their data
publicly available. Some of these are already in the SILVA database, but many
are only available in supplementary materials or on lab websites. To generate
the pooled fasta and metadata files we run the following. Note that because
we're scraping data out of some supplements these scripts assume that you have
access to the journals...

```{r get_emirge, engine="bash"}
bash code/get_emirge_fasta.sh
bash code/get_emirge_metadata.sh
```

This will bring in 81,616 sequences: 81608 from bacteria, 7 from archaea, and 1 from a eukaryote. We'll ignore the eukaryote. The `code/get_emirge_fasta.sh` script split the sequences by domain and put the fasta sequences into `data/mothur/` for further processing. We need to process these sequences similar to what we did with the single cell data.

```{r process_emirge, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=data/mothur/emirge.bacteria.fasta, reference=data/mothur/bacteria.good.fasta);
        screen.seqs(fasta=current, start=2000, end=14459, maxambig=2, minlength=1200);
        classify.seqs(fasta=data/raw/EMIRGE.fasta, reference=data/mothur/bacteria.good.fasta, taxonomy=data/mothur/bacteria.good.tax, cutoff=80, processors=8)"
```

@@

#need to change the name of this sequence to make it clear that it was not cultured
rownames(metadata)[rownames(metadata) == 'AJ224540.MxeCultu'] <- 'AJ224540.UncMxeCultu'
